---
title: "My R Markdown Primer"
author: "Joe Clasby"
date: "April 12, 2026"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# Introduction

R Markdown is a tool that lets you combine regular writing, R code, and
output in one document. It is useful because you can explain your work,
run your analysis, and show results all in the same place. This makes
projects easier to organize and helps support reproducible analysis.

This document shows how narrative text, math expressions, and code
chunks can all work together. Instead of writing a separate report after
doing the analysis, R Markdown allows the report and the analysis to
stay connected.

# Markdown Paragraph

One thing I noticed about R Markdown is that it feels more efficient
than writing a plain report by itself. I can type explanations in normal
paragraph form, then immediately add code underneath to back up what I
am saying. That makes the document feel more organized and more honest,
because the results are coming directly from the code rather than being
copied over manually.

# LaTeX Math

Here is an inline math example: $\alpha + \beta = \gamma$

Here is a displayed equation:

$$
\bar{x} = \frac{\sum_{i=1}^{n} x_i}{n}
$$

```{r}
library(ggplot2)
data(mtcars)

head(mtcars)
```

```{r}
summary(mtcars)
```

```{r}
ggplot(data = mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(
    title = "Car Weight vs Miles Per Gallon",
    x = "Weight",
    y = "Miles Per Gallon"
  )
```
